Modelling last glacial cycle ice dynamics in the Alps

### 2017-12-27 articles/cycle/alps-cycle.tex
Add discussion of ice domes.

    Finally, self-sustained ice domes characteristic of ice caps are modelled
    in two locations over Flüela Pass and Ötztal (Fig.~\ref{fig:lgmvel}a).
    \todo{Compare to Florineth.}
    Except for too extensive ice cover in the easternmost part of the model
    domain (Sect.~\ref{sec:extent}), there is generally a good agreement
    between transfluences observed in the geomorphology and the model results.
    Both depict the LGM Alpine ice flow pattern as an intermediate between that
    of a topography-controlled ice field, and that of a self-sustained ice cap.

>>>>

    Finally, self-sustained ice domes characteristic of ice caps are modelled
    in two locations over Flüela Pass and Ötztal (Fig.~\ref{fig:lgmvel}a).
    These modelled ice domes exhibit radial ice surface slopes and radial flow
    velocities crosscutting the underlying topographic troughs and ridges.
    On the one hand, ice-dispersal centres previously labelled as ice domes
    in the upper Rhone and Rhine Valley \citep{Florineth.Schluchter.1998,
    Kelly.etal.2004, Bini.etal.2009} feature as mere ice divides in our
    simulation. On the other hand, the modelled ice dome over Flüela Pass
    overlaps with the previously mapped Engadine ice dome
    \citep{Florineth.1998}, although its centre is modelled ca.~20\,km north of
    that indicated by geomorphology \citep[Fig.~3]{Florineth.1998}.

    Except for too extensive ice cover in the easternmost part of the model
    domain (Sect.~\ref{sec:extent}), there is generally a good agreement
    between transfluences observed in the geomorphology and the model results.
    Both depict the LGM Alpine ice flow pattern as an intermediate between that
    of a topography-controlled ice field, and that of a self-sustained ice cap.
